Causal Compatibility Inequalities Admitting Quantum Violations in the Triangle Structure

### 2020-07-14 CCIAQVTS/CCIAQVTS.tex
removed all non-PRA instances of 'new'

    Fritz's problem is concerned with how to find and recognize nonclassical quantum distributions specifically for the Triangle structure. The original proof of nonclassicality essentially recycled Bell's theorem, and was limited by the requirement of perfect correlations~\cite{Fritz_2012}. Fritz's problem, as originally stated, does not require that the \emph{type} of nonclassicality be novel to the Triangle structure, rather, only that the proof should avoid Bell's theorem. \Cref{sec:preliminary_research} delineates our initial, failed attempts at resolving Fritz's problem; \Cref{sec:found_inequalities} reports our eventual success, via the discovery of new causal compatibility inequalities.

    Though not explicit, we read in the spirit of Fritz's problem a desideratum for the discovery of a truly novel form of nonclassicality for the Triangle structure. Such a discovery would presumably lead to an understanding of new advantages of quantum resources in network structures; this related problem has attracted attention and conjecture \cite{Gisin_2017}, but remains open. We attempt to make progress on this problem by leveraging the new causal compatibility inequalities derived herein, but \Cref{sec:optimizations} delineates that is effort was plagued by instabilities in our numerical optimization which we have not yet overcome. Consequently, \Cref{sec:fritz_problem_revisit} discusses potential avenues for rigorously reformulating Fritz's problem in order to best capture this desire for novel quantum nonclassicality.

@@

    \subsection{The Symmetric Web Inequality}
    In \cref{sec:optimizations} we will consider numerically optimizing our inequalities over quantum strategies, seeking violations, towards the desired end-goal of discovering new forms of nonclassicality in the Triangle structure. Of course, if some inequality achieves its optimal quantum violation on a distribution qualitatively similar to $\prob[\fritz]$, then such an inequality is unlikely to lead us to discover nonclassicality of a type different than $\prob[\fritz]$. Indeed, we will show that the previous pair of $I\tsb{WagonWheel}$ and $I\tsb{Web}$, which were both specifically curated to demonstrate the incompatibility of $\prob[\fritz]$, apparently achieve maximum quantum violation on distributions very similar to $\prob[\fritz]$ itself.

@@

    When specifically concerned with entanglement resources, Bell structure nonclassicality exploits the entanglement of a \textit{single} bipartite quantum state. Unlike the Bell structure in~\Cref{fig:bell_structure}, the observable nodes of the Triangle structure in~\Cref{fig:triangle_structure} have access to potentially \textit{three} different bipartite quantum states. As noted in~\cite{Fritz_2012}, the Fritz distribution can be implemented using only a \textit{single} entangled state.\footnote{Of course there exists implementations that make use of three entangled states but at \textit{minimum}, one is necessary.} Therefore, it becomes reasonable to propose that any quantum nonclassicality in the Triangle structure that \textit{requires} entanglement in \textit{at least two} shared states constitutes nonclassicality distinct from Bell nonclassicality. At first, one might suspect that finding such distributions would affirmatively demonstrate a new form of entanglement resource unique to the Triangle structure. Unfortunately, this is not the case. By increasing the cardinality of each variable $A, B, C$ to $4^{3} = 64$, it is possible to generate a distribution that is nonclassical yet quantum and requires \textit{all three} of the shared resources to be entangled. This can be accomplished by superimposing three copies of statistically independent Fritz distributions to the Triangle structure, each of which utilizes a distinct party to announce the corresponding measurement pseudo-settings. Such a distribution would require entanglement in all three quantum states; under this construction, the removal of any entangled resource would render the distribution quantum-inaccessible\footnote{This observation was original provided by Miguel Navascués.}. Consequently, demanding the necessity of entanglement in every shared state is insufficient for finding novel nonclassicality.

@@

    Unlike $\prob^{\ImInj[\graph]{\graph'}}$, which is non-contextual by construction, $\prob^{\Inj[\graph]{\graph'}}$ contains overlapping marginals meaning its contextuality remains unknown and must be determined using any of the techniques discussed in~\cref{sec:marginal_satisfiability}. More importantly, the Inflation Technique introduces new constraints relating to the ai-expressible sets. In practice, the equality constraints implied by $\AIExpr[\graph]{\graph'}$ permits one to construct a marginal model defined over the ai-expressible sets $\AIExpr[\graph]{\graph'}$ resulting in greater resolution in classifying the compatibility of $\prob[\nodes_O]$. In summary, the Inflation Technique partially transforms the compatibility problem into a marginal problem, wherein one can solve the marginal problem (\cref{sec:marginal_satisfiability}) to either determine the compatibility of an observable distribution $\prob[\nodes_O]$ with $\graph$ or derive compatibility inequalities for $\graph$, the latter of which is discussed in \cref{sec:deriving_inequalities}.

>>>>

    Fritz's problem is concerned with how to find and recognize nonclassical quantum distributions specifically for the Triangle structure. The original proof of nonclassicality essentially recycled Bell's theorem, and was limited by the requirement of perfect correlations~\cite{Fritz_2012}. Fritz's problem, as originally stated, does not require that the \emph{type} of nonclassicality be novel to the Triangle structure, rather, only that the proof should avoid Bell's theorem. \Cref{sec:preliminary_research} delineates our initial, failed attempts at resolving Fritz's problem; \Cref{sec:found_inequalities} reports our eventual success, via the discovery of different causal compatibility inequalities.

    Though not explicit, we read in the spirit of Fritz's problem a desideratum for the discovery of a truly novel form of nonclassicality for the Triangle structure. Such a discovery would presumably lead to an understanding of different advantages of quantum resources in network structures; this related problem has attracted attention and conjecture \cite{Gisin_2017}, but remains open. We attempt to make progress on this problem by leveraging the causal compatibility inequalities derived herein, but \Cref{sec:optimizations} delineates that is effort was plagued by instabilities in our numerical optimization which we have not yet overcome. Consequently, \Cref{sec:fritz_problem_revisit} discusses potential avenues for rigorously reformulating Fritz's problem in order to best capture this desire for novel quantum nonclassicality.

@@

    \subsection{The Symmetric Web Inequality}
    In \cref{sec:optimizations} we will consider numerically optimizing our inequalities over quantum strategies, seeking violations, towards the desired end goal of discovering different forms of nonclassicality in the Triangle structure. Of course, if some inequality achieves its optimal quantum violation on a distribution qualitatively similar to $\prob[\fritz]$, then such an inequality is unlikely to lead us to discover nonclassicality of a type different than $\prob[\fritz]$. Indeed, we will show that the previous pair of $I\tsb{WagonWheel}$ and $I\tsb{Web}$, which were both specifically curated to demonstrate the incompatibility of $\prob[\fritz]$, apparently achieve maximum quantum violation on distributions very similar to $\prob[\fritz]$ itself.

@@

    When specifically concerned with entanglement resources, Bell structure nonclassicality exploits the entanglement of a \textit{single} bipartite quantum state. Unlike the Bell structure in~\Cref{fig:bell_structure}, the observable nodes of the Triangle structure in~\Cref{fig:triangle_structure} have access to potentially \textit{three} different bipartite quantum states. As noted in~\cite{Fritz_2012}, the Fritz distribution can be implemented using only a \textit{single} entangled state.\footnote{Of course there exists implementations that make use of three entangled states but at \textit{minimum}, one is necessary.} Therefore, it becomes reasonable to propose that any quantum nonclassicality in the Triangle structure that \textit{requires} entanglement in \textit{at least two} shared states constitutes nonclassicality distinct from Bell nonclassicality. At first, one might suspect that finding such distributions would affirmatively demonstrate a form of entanglement resource unique to the Triangle structure. Unfortunately, this is not the case. By increasing the cardinality of each variable $A, B, C$ to $4^{3} = 64$, it is possible to generate a distribution that is nonclassical yet quantum and requires \textit{all three} of the shared resources to be entangled. This can be accomplished by superimposing three copies of statistically independent Fritz distributions to the Triangle structure, each of which utilizes a distinct party to announce the corresponding measurement pseudo-settings. Such a distribution would require entanglement in all three quantum states; under this construction, the removal of any entangled resource would render the distribution quantum-inaccessible\footnote{This observation was original provided by Miguel Navascués.}. Consequently, demanding the necessity of entanglement in every shared state is insufficient for finding novel nonclassicality.

@@

    Unlike $\prob^{\ImInj[\graph]{\graph'}}$, which is non-contextual by construction, $\prob^{\Inj[\graph]{\graph'}}$ contains overlapping marginals meaning its contextuality remains unknown and must be determined using any of the techniques discussed in~\cref{sec:marginal_satisfiability}. More importantly, the Inflation Technique introduces constraints relating to the ai-expressible sets. In practice, the equality constraints implied by $\AIExpr[\graph]{\graph'}$ permits one to construct a marginal model defined over the ai-expressible sets $\AIExpr[\graph]{\graph'}$ resulting in greater resolution in classifying the compatibility of $\prob[\nodes_O]$. In summary, the Inflation Technique partially transforms the compatibility problem into a marginal problem, wherein one can solve the marginal problem (\cref{sec:marginal_satisfiability}) to either determine the compatibility of an observable distribution $\prob[\nodes_O]$ with $\graph$ or derive compatibility inequalities for $\graph$, the latter of which is discussed in \cref{sec:deriving_inequalities}.
